Measurement and Probability in Fuzzy Quantum Theories

### 2017-04-19 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Fix typos...

\begin{thm}\cite{GilboaSchmeidler1994,Grabisch2016}For every classical
IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ and any random variable~$X:\Omega\rightarrow\mathbb{R}$,
$\bar{\mu}$ is convex if and only if 
\begin{equation}
\int X\rmd\bar{\mu}=\left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu\right]\textrm{ .}
\end{equation}
\end{thm}

@@

Consider a quantum IVPM~$\bar{\mu}$ such that $l:\events\rightarrow\left[0,1\right]$
and $r:\events\rightarrow\left[0,1\right]$ are the left-end and the
right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$.
Given the same observable with an extra condition~
\[
x_{N^{-}}\le x_{N^{-}+1}\le\ldots\le x_{-2}\le x_{-1}\le x_{0}=0\le x_{1}\le x_{2}\le\ldots\le x_{N^{+}-1}\le x_{N^{+}}
\]
and let $P_{i}'=\sum_{j\ge i}P_{j}\in\events$ for $i>0$, and $P_{i}'=\sum_{j\le i}P_{j}\in\events$
for $i<0$, we can combine equation~(\ref{eq:interval-expectation})
and (\ref{eq:quantum-expectation}) to define the expectation value
of $\mathbf{O}$ with respect to $\bar{\mu}$ as
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{i=1}^{N}\lambda_{i}\left[l\left(P_{i}'\right)-l\left(P_{i+\mathrm{sign}\left(i\right)}'\right),r\left(P_{i}'\right)-r\left(P_{i+\mathrm{sign}\left(i\right)}'\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
\end{equation}
Let $\events\left(\mathbf{O}\right)$ denote the minimal sub-event
space containing $\left\{ P_{i}\right\} _{i=1}^{N}$. Then, we have
the corresponding theorem.

>>>>

\begin{thm}\cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}For
every classical IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ and
any random variable~$X:\Omega\rightarrow\mathbb{R}$, $\bar{\mu}$
is convex if and only if 
\begin{equation}
\int X\rmd\bar{\mu}=\left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu\right]\textrm{ .}
\end{equation}
\end{thm}

@@

Consider a quantum IVPM~$\bar{\mu}$ such that $l:\events\rightarrow\left[0,1\right]$
and $r:\events\rightarrow\left[0,1\right]$ are the left-end and the
right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$.
Given the same observable with an extra condition~
\[
\lambda_{N^{-}}\le\lambda_{N^{-}+1}\le\ldots\le\lambda_{-2}\le\lambda_{-1}\le\lambda_{0}=0\le\lambda_{1}\le\lambda_{2}\le\ldots\le\lambda_{N^{+}-1}\le\lambda_{N^{+}}
\]
and let $P_{i}'=\sum_{j\ge i}P_{j}\in\events$ for $i>0$, and $P_{i}'=\sum_{j\le i}P_{j}\in\events$
for $i<0$, we can combine equation~(\ref{eq:interval-expectation})
and (\ref{eq:quantum-expectation}) to define the expectation value
of $\mathbf{O}$ with respect to $\bar{\mu}$ as
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{i=1}^{N}\lambda_{i}\left[l\left(P_{i}'\right)-l\left(P_{i+\mathrm{sign}\left(i\right)}'\right),r\left(P_{i}'\right)-r\left(P_{i+\mathrm{sign}\left(i\right)}'\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
\end{equation}
Let $\events\left(\mathbf{O}\right)$ denote the minimal sub-event
space containing $\left\{ P_{i}\right\} _{i=1}^{N}$. Then, we have
the corresponding theorem.
